Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Successfully merged the retro age, gender and employ graphs

This will plot the stacked bar charts of the gender, age, employment, ethnicity and diagnosis variables together.

```{r Plot histograms together}

#Adding any more makes it look awful
ggarrange(retro_age_plot, retro_gender_plot, retro_employ_plot,
          labels = c("", "", ""),
          ncol = 2, nrow = 2)

>>>>

```{r Plot age gender and employ histograms together}

arranged_gender_plot <- retro_gender_plot +
  theme(legend.position = "none") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   expand = expansion(mult = c(0.3, 0.4)))

arranged_employ_plot <- retro_employ_plot +
  theme(legend.position = "none") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))

#Combine retro age, gender and employ together
ggarrange(retro_age_plot, 
          ggarrange(arranged_gender_plot, arranged_employ_plot, ncol = 2), 
          nrow = 2,
          common.legend = TRUE)

```{r Plot retro diagnosis and ethnicity together}
